---
title: "HW 1"
author: "Rick Boelen, Haley Lai, Hwang Min Yu "
date: "4/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Data Setup
current.path = "/Users/Hwang Min/Desktop/UCSD/Math 189/Homework/01"
setwd(current.path)
getwd()


data <- read.table("babies.txt", header=TRUE)
View(data)
summary(data)


smoker.ind <- which(data['smoke'] == 1)
data.smoke <- data[smoker.ind,]
View(data.smoke)
summary(data.smoke$bwt)

nonsmoker.ind <- which(data['smoke'] == 0)
data.nonsmoke <- data[nonsmoker.ind,]
View(data.nonsmoke)
summary(data.nonsmoke$bwt)

# Data Analysis
```
Basic Graphs (shape)
```
hist(data.smoke$bwt, breaks = 20,xlim=c(60, 180),freq = FALSE, main = "Distribution of the weight of baby for mothers who smoke", xlab = "Baby Weight in Ounces")
abline(v=88, col="red", lwd = 2)

hist(data.smoke$bwt, breaks = 20,xlim=c(60, 180),freq = FALSE, main = "Distribution of the weight of baby for mothers who smoke", xlab = "Baby Weight in Ounces")
curve(dnorm(x,mean = mean(data.smoke$bwt),sd=sd(data.smoke$bwt)), add=TRUE,col="red",lwd=2)

hist(data.nonsmoke$bwt, breaks = 20, xlim=c(60,180),freq = FALSE, main = "Distribution of the weight of baby for mothers who do not smoke", xlab = "Baby Weight in Ounces")
abline(v=88, col="red", lwd = 2)

hist(data.nonsmoke$bwt, breaks = 20, xlim=c(60,180),freq = FALSE, main = "Distribution of the weight of baby for mothers who do not smoke", xlab = "Baby Weight in Ounces")
curve(dnorm(x,mean = mean(data.nonsmoke$bwt),sd=sd(data.nonsmoke$bwt)), add=TRUE,col="red",lwd=2)

```
Mean and Median (location)
```
mean(data.smoke$bwt)
mean(data.nonsmoke$bwt)
mean.diff <- abs(mean(data.smoke$bwt) - mean(data.nonsmoke$bwt))
mean.diff

median(data.smoke$bwt)
median(data.nonsmoke$bwt)

nrow(data.smoke)
nrow(data.nonsmoke)
```
Standard Deviation (spread)
```
sd(data.smoke$bwt)
sd(data.nonsmoke$bwt)

```
InterQuartile Range (spread)
```
IQR(data.smoke$bwt)
IQR(data.nonsmoke$bwt)

```
Kurtosis coefficient:
how pronounced is the peak of the distribution
```
kurtosis <- function(x){
 x_std <- (x-mean(x))/sd(x)
 return(mean(x_std^4))
}
kurtosis(data.smoke$bwt)
kurtosis(data.nonsmoke$bwt)


# Simulation studies

n=length(data.smoke$bwt)
fill_kurtosis_smoke <- rep(NA,1000)
for(i in 1:1000){
  fill_kurtosis_smoke[i] <- kurtosis(rnorm(n))
}


```
Expectation = obseration statistic of Kurtosis statistic
```

m=length(data.nonsmoke$bwt)
fill_kurtosis_nonsmoke <- rep(NA,1000)
for(i in 1:1000){
  fill_kurtosis_nonsmoke[i] <- kurtosis(rnorm(m))
}
hist(fill_kurtosis_smoke,main = "Sample Distribution of Kurtosis Coefficient for mothers who smoke")
hist(fill_kurtosis_nonsmoke, main = "Sample Distribution of Kurtosis Coefficient for mothers who do not smoke")




# Frequency

table(data.smoke$bwt < 88)
prop.table(table(data.smoke$bwt < 88))

table(data.nonsmoke$bwt < 88)
prop.table(table(data.nonsmoke$bwt < 88))

```
Reliability check
```
table(data.smoke$bwt < 85)
prop.table(table(data.smoke$bwt < 85))
table(data.nonsmoke$bwt < 85)
prop.table(table(data.nonsmoke$bwt < 85))

table(data.smoke$bwt < 93)
prop.table(table(data.smoke$bwt < 93))
table(data.nonsmoke$bwt < 93)
prop.table(table(data.nonsmoke$bwt < 93))


# Additional analysis

clean.index <- which(data$age == 99)
cleandata.index <- setdiff(rownames(data), clean.index)
clean.table <- data[cleandata.index,]

clean.smoke.ind <- which(clean.table['smoke'] == 1)
clean.smoke <- clean.table[clean.smoke.ind,]
clean.smoke.young.ind <- which(clean.smoke["age"] < 26)
clean.smoke.old.ind <- which(clean.smoke["age"] >= 26)
clean.smoke.young <- clean.smoke[clean.smoke.young.ind,]
clean.smoke.old <- clean.smoke[clean.smoke.old.ind,]

clean.nonsmoke.index <- which(clean.table['smoke'] == 0)
clean.nonsmoke <- clean.table[clean.nonsmoke.index,]
clean.nonsmoke.old.ind <- which(clean.nonsmoke["age"] > 26)
clean.nonsmoke.young.ind <- which(clean.nonsmoke["age"] <= 26)
clean.nonsmoke.young <- clean.nonsmoke[clean.nonsmoke.young.ind,]
clean.nonsmoke.old <- clean.nonsmoke[clean.nonsmoke.old.ind,]

prop.table(table(clean.nonsmoke.old$bwt < 88))
prop.table(table(clean.nonsmoke.young$bwt < 88))
prop.table(table(clean.smoke.old$bwt < 88))
prop.table(table(clean.smoke.young$bwt < 88))
```{r pressure, echo=FALSE}

```
